Combined Task and Motion Planner through an Interface Layer

### 2015-05-12 documentation/ps4.tex
updates to improvements section

@@

@@

>>>>

Every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

@@

This enables us to find plans a lot more quickly: whenever a plan is possible, we find it by backtracking search.  
Often, the first pose that's tried won't be viable but another pose will.  
Partial trajectory mode will only try the first pose before giving up and identifying blocking objects.
If partial trajectory mode is continually used, then often the plans created are much longer than necessary just because an invalid first pose is chosen when other options would have worked fine.
Using the full backtracking search on each new high level plan avoids this problem.

@@

\subsection{Future improvements}

The interface layer winds up making a lot of duplicate calls to the motion planner.
If the interface layer kept track of more state, perhaps via some memoization process of poses and actions, it would be able to save a lot of motion call attempts.
Furthermore, when the interface layer finds obstructing objects, it finds obstructing objects for a particular pose.  
If that pose were stored, then the interface layer would never attempt to use a different pose which might have different blocking objects, and would instead directly use the pose that the plan was optimized for.
